%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
	{Software Development Intern} % Job title
	{Ansys} % Organization
	{Waterloo, ON} % Location
	{May, 2022 - Apr, 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			%\item {Tech Stack: AngularJS, ASP.NET, MongoDB.}
			\item {Implemented a robust batch user-subscription management feature in a \textbf{RESTful} web architecture incorporating \textbf{AngularJS} and \textbf{ASP.NET}.}
			\item {Delivered high-quality code following SOA principles accompanied with \textbf{unit tests} in \textbf{C\#}.}
			\item {Identified and Addressed data encryption deficiencies in the front-end design based on \textbf{MVC design pattern} through refactoring, enhancing data security and integrity.}
			%\item {Collaborated with a colleague to investigate and resolve performance issues on a high-demanding API endpoint through peer coding, resulting in improved response times and overall system performance.}
			\item {Accomplished context-specific tasks such as handling content submission requests, involving \textbf{MongoDB} data management and seamless email communication with external submitters, streamlining the content management process.}
			\item {Developed a comprehensive workflow diagram for a brand new marketplace platform using \textbf{MS Visio}, providing a high-level \textbf{architecture design} for the project team and stakeholders.}
		\end{cvitems}
	}

  \cventry
    {Full Stack Developer} % Job title
    {Fundscraper Capital Inc.} % Organization
    {Toronto, ON} % Location
    {Sep, 2021 - Dec, 2021} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			%\item {Technical takeaways: ReactJS, PHP, PostgreSQL.}
			\item {Generalized and Customized frontend UI components using object-oriented principles in \textbf{TypeScript} and \textbf{React}, improving user interface consistency and code reusability.}
			\item {Maintained and Enhanced automated tests daily, employing \textbf{Selenium} and \textbf{Cucumber.js} for end-to-end testing and \textbf{Postman} for API testing. Utilized data isolation and validation strategies to reduce test fragility and ensure reliable results.}
			\item {Developed and Implemented a comprehensive procedure for checking customer sanction status, from fetching and parsing sanction lists with \textbf{PHP} and \textbf{MS SQL Server} to comparing our customers and identifying potential matches.}
			\item {Migrated essential business logic from a \textbf{PHP-jQuery} codebase to a new \textbf{React} application, facilitating a seamless transition and continuity of business operations.}
		\end{cvitems}
    }

  \cventry
	{Software Developer} % Job title
	{Indie Travel} % Organization
	{Toronto, ON} % Location
	{Jan, 2021 - Apr, 2021} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			%\item {Technical takeaways: React, Typescript, Docker}
			\item {Developed the web application's onboarding interface using \textbf{React} and \textbf{Material-UI} to enhance user experience.}
			\item {Programmed a tool in the app's front-end to enable user to interact with another tour provider's application. Coded and tested target application's Api using asynchronous \textbf{TypeScript} and \textbf{Postman}.}
			\item {Implemented a user avatar system leveraging \textbf{AWS S3} services, providing a more personalized user experience.}
			\item {Structured the user help center by integrating Ghost CMS and \textbf{Docker}, increasing user support and accessibility.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
